\part{Bornologies}

As mentioned in the introduction, the category of Banach spaces \(\mathsf{Ban}\) is the smallest meaningful category in which functional analysis combines well with homological algebra. Specifically, it is a closed, symmetric monoidal category with respect to the completed projective tensor product and the Hom-space equipped with the operator norm.  However, the category of Banach spaces is not closed under, say, projective limits, so that important algebras such as \(\Cont^\infty(M)\) are not included in it. There are two ways of remedying this -- working with the \emph{pro-completion} and the \emph{ind-completion}. The former category includes complete, locally convex topological vector spaces, but still lacks an internal Hom functor that is right adjoint to the completed projective tensor product. What we therefore instead look at is the category \(\mathsf{Ind}(\mathsf{Ban})\) of inductive systems of Banach spaces. It is also worth noting that so far we have not fixed a base field over which we propose to do functional analysis -- this is manifestly deliberate. We wish to develop a framework that yields desirable categorical outcomes no matter what the base field or ring may be.  \textbf{Write Leitfaden for chapter.}


\chapter{Concrete models for bornologies}

The category of inductive systems \(\mathsf{Ind}(\mathsf{Ban})\), while having useful categorical properties that we will eventually see, has the drawback that it is not a concrete category. It turns out, however, that it is equivalent (in a sense that will be made precise) to a concrete category. This category can alternatively be described by objects that are vector spaces with additional structure, axiomatically referred to as ``bounded sets''. So far, this alternative characterisation has been explicitly worked out in the case where the base field is \(\R\), \(\C\) with their Euclidean topologies (colloquially referred to as ``Archimedean'' fields) and a complete, discrete valuation field \(\dvf\) (such as \(\Q_p\)) with its usual ``nonarchimedean'' valuation.  

\section{Bornological functional analysis in the archimedean case}

\input{bornologies/lecture-1}

\input{bornologies/lecture-2}

\input{bornologies/lecture-3}

\input{bornologies/lecture-4}

\input{bornologies/lecture-5}

\input{bornologies/lecture-6}

\input{bornologies/lecture-7}

\input{bornologies/lecture-8}

\input{bornologies/exercises-1.1}

\section{Bornological functional analysis in the nonarchimedean case}

\chapter{Abstract models for bornologies}

\input{bornologies/placeholder}